Approximation as Differentiation: Notes

### 2025-05-25 main/category-of-families.tex
Progress, bit clumsy still..

We can verify that $\tangents$ is functorial, regardless of whether the linear maps $\RR^m \linearto \RR^n$
happen to be derivatives. But if $f_2(x)$ is the derivative of $f_1$ at $x$ for any $x \in \RR^m$ and
similarly for $g$ then the derivatives compose according to the forward chain rule and $(g \comp f)_2(x)$ is
the derivative of $(g \comp f)_1$ at $x$. Thus this setup provides a way of computing the forward derivative
of a composite function automatically, without computing each constituent $f(x)$ more than once, so long as
the primitive operations of the system can provide derivatives. An efficient implementation of \GPS based on
$\Fam(\LatGal)$ (\secref{fam:galois-slicing} above) would most likely apply a similar optimisation to avoid
recomputing $f(x)$ at each step during forward slicing.

>>>>

We can verify that $\tangents$ is functorial, regardless of whether the linear maps $\RR^m \linearto \RR^n$
happen to be derivatives. But if $f_2(x)$ is the derivative of $f_1$ at $x$ for any $x \in \RR^m$ and
similarly for $g$ then the derivatives compose according to the forward chain rule and $(g \comp f)_2(x)$ is
the derivative of $(g \comp f)_1$ at $x$. Thus this setup provides a way of computing the forward derivative
of a composite function without have to recompute the function itself, so long as all atomic operations
provide derivatives. An efficient implementation of \GPS based on $\Fam(\LatGal)$ (\secref{fam:galois-slicing}
above) would most likely apply a similar optimisation to avoid recomputing $f(x)$ at each step during forward
slicing.
